The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-27 paper.tex
update

%\begin{enumerate}
%  \item Assumptions on gravity:
%    \begin{enumerate}
%      \item We use the potential of isothermal slab, symmetric about $z=0$ and\
%            supported by gas pressure and by under its own self-gravity,\
%            to mimic the realistic potential of Galactic bulge.
%      \item The ISM disk and atmosphere are subjected to the fixed external potential\
%            due to a disk bulge and dark matter halo.
%      \item In addition to the gravitational interaction, we ignore other interactions between stars and gases.
%      \item We also ignore the self-gravity of the ISM disk and of the atmosphere.
%      \item We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
%      \item We use the potential of isothermal slab to mimic the gravitational potential due to the stellar bulge.
%      \item The interface between cold ISM disk and atmosphere is parallel to the Galactic plane and is pressure balanced.
%    \end{enumerate}
%\end{enumerate}
%
%
%
%\begin{enumerate}
%\item Fixed external gravitational potential:
%  \begin{enumerate}
%    \item Bulge potential:
%      \begin{enumerate}
%       \item Peak density: $\rho_{\text{bulge}}^{\text{peak}}=4\times 10^{-24}$ g/cm$^3$.
%       \item Potential (isothermal slab):
%         \begin{equation}
%           \Phi_{\text{bulge}}=\
%           2\sigma^2_{\text{bulge}}\
%           \ln\cosh\left(z\sqrt{\frac{2\pi G\rho_{\text{bulge}}^{\text{peak}}}{\sigma^2_{\text{bulge}}}}\right),
%         \end{equation}
%          where $\displaystyle \sigma_{\text{bulge}}=\
%                \sqrt{\frac{k_{B}T_{\text{bulge}}}{m}}=100$ km/s \citep{velocity-dispersion-MW}.
%      \end{enumerate}
%
%    \item Dark logarithmic halo potential:
%         \begin{equation}
%           \Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right),
%         \end{equation}
%         where $v_{\text{halo}}=131.5$ km/s, $d_{\text{h}}=12$ kpc \citep{Yang2013}.
%
%    \item Total potential: $\Phi_{\text{total}}=\Phi_{\text{bulge}}+\Phi_{\text{halo}}$.
%  \end{enumerate}
%
%
%\item Clumpy cold disk:
%  \begin{enumerate}
%    \item Dimension: $14\times14\times0.2$ kpc. i.e. Scale height, $z_{0}=100$ pc. \citep{peak-ism-density}
%    \item Peak mass density: $\rho_{\text{disk}}^{\text{peak}}=10^{-23}$ g/cm$^3$. \citep{peak-ism-density}
%    \item Average temperature: $T_{\text{disk}}=10^{3}$ K. \citep{peak-ism-density}
%    \item Average mass density:
%          \begin{equation}
%             \rho_{\text{disk}}=\rho_{\text{disk}}^{\text{peak}}
%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right].
%             \label{disk-density}
%          \end{equation}
%
%    \item Pressure: $\displaystyle p_{\text{disk}}=\rho_{\text{disk}}T_{\text{disk}}$.
%
%    \item The clumpy cuboid, using the publicly\
%          available pyFC code\footnote{\url{https://pypi.python.org/pypi/pyFC}},\
%          are described by a log-normal distribution with mean 1.0 and variance 5.0.\
%          Also, the power spectrum of the clumpy cuboid is characterized by $k_{\text{min}}$ and $\beta$,\
%          where $k_{\text{min}}$ sets the maximum cloud size within the clumpy cuboid,\
%          and $\beta$ is the slope of power spectrum in Fourier space.
%          In this paper, we set $\beta=-5/3$ and $k_{\text{min}}=375$ to follow the Kolmogorov spectrum\
%          and to limits the maximum size of an individual cloud to approximately 25 pc.
%
%    \item The clumpy disk is then constructed by multiplying a fractal cuboid with \Cref{disk-density}.
%
%    \item The clouds and voids within clumpy disk are pressure balanced.
%  \end{enumerate}
%
%
%\item Isothermal atmosphere:
%  \begin{enumerate}
%     \item The region outside the clumpy cold disk is atmosphere.
%     \item $T_{\text{atmp}}=10^{6}$ K. \citep{temperature-MW}
%     \item Density:
%          \begin{equation}
%             \rho_{\text{atmp}}=\rho_{\text{atmp}}^{\text{peak}}
%             \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right],
%             \label{atmosphere-density}
%          \end{equation}
%          where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
%          and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.
%  \end{enumerate}
%
%
%
%\end{enumerate}
%

\subsection{Jet injection}
  We resolve the jet source located at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

 \begin{enumerate}
    \item Why the overall structure is insensitive to jet direction?
      \begin{enumerate}
        \item Jet source size.
        \item Cold disk.
        \item Large pressure gradient along z-dircetion.
      \end{enumerate}
 \end{enumerate}

>>>>

% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
% We also ignore the self-gravity of the ISM disk and of the atmosphere.
% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
%

\subsection{Jet injection}
  The core of this work is to release the caveat that the jet direction must be perpendicular to the Galactic plane.\
  We resolve the jet source at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

 \begin{enumerate}
    \item Why the overall structure is insensitive to jet direction?
      \begin{enumerate}
        \item Jet source size.
        \item Cold disk.
        \item Large pressure gradient along z-direction.
      \end{enumerate}
 \end{enumerate}
